Multiphyscis modeling for the Fluoride-salt-cooled High-temperature Reactor (FHR)

### 2018-07-28 paper/main.tex
Updates from ShareLaTeX

\subsubsection{Cross-section generation}
The group-averaged, component-wise neutronic constants, used in the diffusion equations, are generated with the Monte Carlo neutron transport code Serpent using the nuclear data library ENDF/B-VII.0. 
In order to perform transient analysis, these cross-sections need to be paramatrized as functions of reactor operating conditions via a process called computer experiments, in which one runs a Monte Carlo model with a sample of operating conditions and fits a function between the resulting cross-sections and the input data.

@@

Unlike liquid salt, the solid fuel elements do not change shape or density in the considered temperature range. 
The change in fuel cross-sections are mainly due to the Doppler broadening of the microscopic cross-sections of the fuel material and exhibit a linear-log function of temperature.  It is important for FHRs to compute the temperature distribution inside TRISO particles and fuel pebbles, and use the temperature profile, instead of an average fuel temperature, to compute cross-sections, because during fast transients such as reactivity induced accidents, the heat does not have time to propagate through the fuel pebbles and to reach the coolant and therefore the core relies on the temperature reactivity feedback inside the TRISO particles to stabilize.
A multiscale cross-section, incorporating a vector of temperatures at different depth in the fuel element, is express as a linear combination of the logarithm of fuel temperatures:

@@

An important parameter for porous media is the porosity, $\epsilon$, defined as the ratio between the volume of the void to the total volume (Equation \ref{eq:pf}). It appears in the mass (Equation \ref{eq:mass}), momentum (Equation \ref{eq:mmtm}) and energy conservation equations (equations \ref{eq:pm_liq} and \ref{eq:pm_sol}) below. Local variation in porosity in a pebble bed, including the drop near the wall due to ordered packing, is not modeled explicitly in the porous media model, but the empirical correlations for pressure loss and heat transfer coefficient incorporate corrections for wall effect.

@@

Other parameters used in equation \ref{eq:mmtm} are:\\
$\rho_f$ = fluid density, kg/m3\\
$\epsilon$ = porosity\\
t = time, s\\
p = pressure, Pa\\
$\mu$ = dynamic viscosity, Pa.s\\
F = body force, $N/m^3$\\
I = identity matrix\\
K = permeability, $m^2$\\
$\beta_F$ = Forcheimer drag coefficient, $kg/m^4$\\

@@

In a typical nuclear reactor, 97\% of the energy is deposited in the fuel while the rest is transported in coolant, reflectors and even shield by long range particles such as neutrons and gammas. 
In the current model, nuclear power is assumed generated inside the solid medium of the fuel region and transferred to the coolant through heat convection. Reflectors have separate coolant channels to maintain the temperature and temperature in outer layers such as graphite reflectors and stainless steel containment has negligible effect on neutronics behaviour, therefore conservative adiabatic boundary condition is applied at the reflector walls and the temperatures of the outer layers are not computed in the coupled simulation. However, they can be computed using the coupled simulation results as boundary conditions.

In a porous media model, the convective heat transfer between the fuel pebbles and the coolant is computed from empirical correlations, whose validation affects directly the credibility of the results. The Wakao correlation (equation \ref{eq:wakao}) \cite{Wakao1979} calculates the convective heat transfer coefficient between pebbles and coolant, with Pr and Re the Prandtl and Reynolds numbers.

@@

The convective heat transfer coefficient can be obtained from the Nussult number, the salt thermal conductivity k and pebble diameter $D_p$ using the relationship in equation \ref{eq:nuh}.

\begin{equation}
  h = \frac{kNu}{D_p}
  \label{eq:nuh}
\end{equation}

Inlet coolant temperature are imposed at the inlet boundary.  This enables modeling of overcooling transient by setting the inlet coolant temperature as a time dependent function. Either flow rate or detailed velocity profile perpendicular to the inlet surface can be imposed as flow straighteners are designed to make sure that the inlet flow is fully developed and the coolant injection channels are designed for prescribed inlet flow conditions.
Zero pressure is set to the outlet surfaces. Slip conditions neglect viscous effects are applied to the walls that contain the fluid.

@@

In order to determine the temperature distribution inside fuel pebbles and TRISO particles, which is crucial for accurately determining the temperature reactivity feedback from the fuel material during transient scenarios, we use the 1-D heat diffusion equation in spherical coordinate to model the heat conduction inside solid fuel elements:

@@

And the resulting equation from a change of variable $U(r,t)=rT(r,t)$ is shown below:

@@

As shown in Figure \ref{fig:model_geom}, the multiphysics reactor core model is composed by three regions: an upper porous region that represents a fuel pebble and flibe salt porous mixture, a lower region with only flibe salt and an outer graphite reflector region. Coupled heat transfer and neutron diffusion equations are solved with homogenized material properties for each region.

@@

A vacuum boundary condition is applied at the outer surfaces of the reflector. And a symmetry boundary condition is used at the core center-line in 2-D axi-symmetrical models.

>>>>

\subsubsection{Cross-section generation}
The group-averaged, component-wise neutronic constants, used in the diffusion equations, are generated with the Monte Carlo neutron transport code Serpent \cite{Serpent2015} using the nuclear data library ENDF/B-VII.0. 
In order to perform transient analysis, these cross-sections are paramatrized as function of reactor operating conditions via a process called computer experiments, in which one runs a Monte Carlo model with a sample of operating conditions and fits a function between the resulting cross-sections and the input data.

@@

Unlike liquid salt, the solid fuel elements do not significantly change shape or density in the considered temperature range. 
The change in fuel cross-sections are mainly due to the Doppler broadening of the microscopic cross-sections of the fuel material and thus exhibit a linear-log function of temperature.  It is important for FHRs to compute the temperature distribution inside TRISO particles and fuel pebbles, and use the temperature profile, instead of an average fuel temperature, to compute cross-sections, because during fast transients such as reactivity induced accidents, the heat does not have time to propagate through the fuel pebbles to reach the coolant and therefore the core relies on the temperature reactivity feedback inside the TRISO particles to stabilize.
A multiscale cross-section, incorporating a vector of temperatures at different depth in the fuel element, is express as a linear combination of the logarithm of fuel temperatures:

@@

An important parameter for porous media is the porosity, $\epsilon$, defined as the ratio between the volume of the void to the total volume (Equation \ref{eq:pf}). It appears in the mass (Equation \ref{eq:mass}), momentum (Equation \ref{eq:mmtm}) and energy conservation equations (Equations \ref{eq:pm_liq} and \ref{eq:pm_sol}) below. Local variation in porosity in a pebble bed, including the drop near the wall due to ordered packing, is not modeled explicitly in the porous media model, but the empirical correlations for pressure loss and heat transfer coefficient incorporate corrections for wall effect.

@@

Other parameters used in Equation \ref{eq:mmtm} are:\\
$\rho_f$ = fluid density, kg/m3\\
$\epsilon$ = porosity\\
t = time, s\\
p = pressure, Pa\\
$\mu$ = dynamic viscosity, Pa.s\\
F = body force, $N/m^3$\\
I = identity matrix\\
K = permeability, $m^2$\\
$\beta_F$ = Forcheimer drag coefficient, $kg/m^4$\\

@@

In a typical nuclear reactor, 97\% of the energy is deposited in the fuel while the rest is transported in coolant, reflectors and even shield by long range particles such as neutrons and gammas. 
In the current model, nuclear power is assumed generated inside the solid medium of the fuel region and transferred to the coolant through heat convection. Reflectors have separate coolant channels to maintain the temperature and temperature in outer layers such as graphite reflectors and stainless steel containment has negligible effect on neutronics behaviour, therefore conservative adiabatic boundary condition is applied at the reflector walls and the temperatures of the outer layers are not computed in the coupled simulation.

In a porous media model, the convective heat transfer between the fuel pebbles and the coolant is computed from Wakao correlation (Equation \ref{eq:wakao}) \cite{Wakao1979}.

@@

@@

In order to determine the temperature distribution inside fuel pebbles and TRISO particles, which is important to compute cross-sections in the fuel region during transient scenarios, we use the 1-D heat diffusion equation in spherical coordinate to model the heat conduction inside solid fuel elements:

@@

After a change of variable $U(r,t)=rT(r,t)$, the equation is transformed to the following form:

@@

As shown in Figure \ref{fig:model_geom}, the multiphysics reactor core model is composed by three regions: an upper porous region that represents a fuel pebble and flibe salt porous mixture, a lower region with only flibe salt and an outer graphite reflector region.

@@

A vacuum boundary condition is applied at the outer surfaces of the reflector. And a symmetry boundary condition is used at the core center-line in 2-D axi-symmetrical models. Inlet coolant flow condition and temperature are imposed at the inlet boundary.  This enables modeling of overcooling transient by setting the inlet coolant temperature as a time dependent function. Zero pressure is set to the outlet surfaces. Slip conditions neglect viscous effects are applied to the walls that contain the fluid.
